Robot programming for dummies

### 2013-06-18 paper.tex
More text

>>>>

Most end user programming systems to date ignore the problem of uncertainty. Some can get away with this because they operate in a simulated world (such as Scratch). Others, which deal with uncertainty in the form of network requests timing or webservices being down, rely on the user to retry the operation as needed. A good user interface paradigm for handling uncertainty will be needed for end user programmed robot control software to be robust.
